\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-08 paper/main.tex
aman's institution
adding totals table
adding material that abid provided

\documentclass[sigconf]{acmart}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

\author{Aman Kumar Singh}
\affiliation{%
 \institution{?}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{?}}
\email{?}

@@

\author{Benjamin Wu}
\affiliation{%
 \institution{?}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{?}}
\email{?}

@@

>>>>

\documentclass[sigconf]{acmart}

\usepackage{multirow}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

\author{Aman Kumar Singh}
\affiliation{%
 \institution{Amrita Vishwa Vidyapeetham}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{India}}
\email{amanks@am.amrita.edu}

@@

\author{Benjamin Wu}
\affiliation{%
 \institution{Purdue University}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{USA}}
\email{wu2059@purdue.edu}

@@

Challenges...

\begin{enumerate}

\sloppy  
\item \textbf{Handling bugs from nighly builds require saving wheels.}
  Many of the reproducible bugs rely on nightly builds since they can
  not be reproduced with any release builds. These nightly builds have
  a limited amount of time when they are publicly available, and they
  are de-indexed and removed after that time. In order to ensure bugs
  that depend on these nightly builds can be reproduced after these
  builds disappear, we save the whl files of these builds.

\item \textbf{Handling bugs in specific GPU-CUDA versions require OS
  changes:} Many of the GPU-related bugs can only be repro
  duced with
  specific GPU builds and specific CUDA builds. Changing different
  virtual environments does not change the CUDA versions of the
  system. That is why we use Docker when a bug relies on a specific
  version of CUDA to be installed in the system.

\end{enumerate}

Table~\ref{...}

\begin{table}
  \centering
  \caption{Characterization of reproducible bugs from \tname.}
\begin{tabular}{lrrr}
  \toprule
  & \multirow{2}{*}{\#} &  \multicolumn{1}{c}{build}          &   \multicolumn{1}{c}{enviroment}  \\
  &   & release-nightly &  venv-docker  \\
  \cmidrule(lr){2-4}
  \jax{} & 44 & 43-1 &  43-1 \\
  \torch{} & 33 & 15-18 & 19-14 \\
  \tf{} & 25 & 24-1 & 25-0 \\
  \midrule
  \multicolumn{1}{c}{$\Sigma$} & 102 & 82-20 & 87-15 \\
  \bottomrule
\end{tabular}
\end{table}
